Draft Figures: 12.23.18

### 2019-01-07 draft_figures_01.07.19.Rmd
5 and 10 year catch averages

>>>>

##Percent Catch ITQ over last 5 Years

##Percent Catch ITQ over last 10 Years
```{r}

fisheries_recent_10years <- read_csv("data/fisheries_recent_10years.csv")

#assuming that when no data is present for itqs/turf that means there are none
fisheries_recent_10years$turf[is.na(fisheries_recent_10years$turf)] <- "FALSE"
fisheries_recent_10years$itq[is.na(fisheries_recent_10years$itq)] <- "FALSE"
fisheries_recent_10years$ivq[is.na(fisheries_recent_10years$ivq)] <- "FALSE"
fisheries_recent_10years$iq[is.na(fisheries_recent_10years$iq)] <- "FALSE"

###creating new column for management; also merging country and the name of species in order to have a way of IDing the fishery to merge with averages in next code peiece
fisheries_turf_itqs_10years_1 <- fisheries_recent_10years %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"
    ))

##get average catch over last 5 years for each fishery
mean_10years <- aggregate(fisheries_turf_itqs_10years_1[, 7], list(fisheries_turf_itqs_10years_1$assess_id_short), mean)
colnames(mean_10years) <- c("assess_id_short", "TenYearCatchAvg")

fisheries_turf_itqs_10years_2 <- select(fisheries_turf_itqs_10years_1, "assess_id_short", "rightsbased", "CommName")

fisheries_turf_itqs_10years <-  merge(fisheries_turf_itqs_10years_2, mean_10years, by.x = "assess_id_short")

turfs_catch <- filter(fisheries_turf_itqs_10years, rightsbased == "2")
itq_catch <- filter(fisheries_turf_itqs_10years, rightsbased == "1")
no_itq_catch <- filter(fisheries_turf_itqs_10years, rightsbased == "0")

sum(turfs_catch$TenYearCatchAvg, na.rm = TRUE)

sum(itq_catch$TenYearCatchAvg, na.rm = TRUE)

sum(no_itq_catch$TenYearCatchAvg, na.rm = TRUE)

```
Turf: 234,000
ITQ: 4,115,210 = 5.1%
